An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Rewrote section of paper that builds the LINEX resample plot.

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q")
@

>>>>

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula= ~ countryAbbrev, alpha=0.05) +
      labs(x=expression(a[0]), y=expression(c[t])) +
       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@
